\textbf{NBA Party}

### 2017-05-20 init_model.rnw
Now creating a betting model for each year in 2012-2016.

<<echo=2:4>>= 
m <- glm(I(team.score > opponent.score) ~ party + odds,
         data = lines[year(date) < 2016], family = 'binomial')
p <- predict(m, newdata = lines[year(date) == 2016], type = 'response')

idx <- which(p < .45)
p1 <- mapply(Predict, prediction = p[idx], 
             vegas = lines[year(date) == 2016, odds][idx],
             MoreArgs=list(threshold = 0.01))
b <- mapply(Bet, our.prediction = p1,
            actual.outcome = lines[year(date) == 2016, team.score > opponent.score][idx],
            odds = lines[year(date) == 2016, odds][idx], SIMPLIFY = T)

sum(b, na.rm = T)

### 
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 4)

>>>>

<<echo=2:4>>=

pdf('mlb_bets_by_season.pdf')
par(mfrow = c(3,2))
lapply(2012:2016, function(yr) {
    m <- glm(I(team.score > opponent.score) ~ party + odds,
             data = lines[year(date) < yr], family = 'binomial')
    p <- predict(m, newdata = lines[year(date) == yr], type = 'response')
    idx <- which(p < .45)
    p1 <- mapply(Predict, prediction = p[idx], 
                 vegas = lines[year(date) == yr, odds][idx],
                 MoreArgs=list(threshold = 0.01))
    b <- mapply(Bet, our.prediction = p1,
                actual.outcome = lines[year(date) == yr, team.score > opponent.score][idx],
                odds = lines[year(date) == yr, odds][idx], SIMPLIFY = T)
    cat(paste0(sum(b, na.rm = T), '\n'))
    ### 
#    pdf(paste0('mlb_bets_', yr, '.pdf'))
    betting.days <- lines[year(date) == yr][idx, date]
    running.prof <- cumsum(ifelse(is.na(b), 0, b))
    plot(x = 1:length(b), y = running.prof, 
         main = paste0('Profits over the ', yr, ' season\n',
                       'Training on 2011-', yr-1, ' data'),
         xlab = 'Game Number', ylab = 'Profit', type = 'l')
    abline(a = 0, b = 0, lty = 3)
    points(x = which.min(running.prof), y = min(running.prof), type = 'p')
    text(x = which.min(running.prof), y = min(running.prof), 
         labels = round(min(running.prof)), pos = 4)
#    dev.off()
})
dev.off()

\includegraphics{mlb_bets_by_season}

m <- glm(I(team.score > opponent.score) ~ party + odds,
         data = lines[year(date) < 2016], family = 'binomial')
p <- predict(m, newdata = lines[year(date) == 2016], type = 'response')
idx <- which(p < .45)
p1 <- mapply(Predict, prediction = p[idx], 
             vegas = lines[year(date) == 2016, odds][idx],
             MoreArgs=list(threshold = 0.01))
b <- mapply(Bet, our.prediction = p1,
                actual.outcome = lines[year(date) == 2016, team.score > opponent.score][idx],
            odds = lines[year(date) == 2016, odds][idx], SIMPLIFY = T)
